Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-30 paper/supp_figs.tex

% \begin{landscape}
{\linespread{1}
  \footnotesize 
\begin{longtable}[c]{ll ccc c}
      %%%%%%%%%%%%%%%%%%%%
      %%% Table header %%%
      %%%%%%%%%%%%%%%%%%%%
      % Upper layer of table header
      \hline
      % Lines inside the header
      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
      \cmidrule(lr){5-6}
       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
      % Lower lines
      \hline
      \vspace{-3pt}
      \endhead
      %%%%%%%%%%%%%%%%%%%%
      %%% Table footer %%%
      %%%%%%%%%%%%%%%%%%%%
      \\[-3pt] \hline
      \caption{Table of circumcision-related questions included in each survey for each sub-Saharan African country. Surveys which did not include a "Circumcision Status" and "Age at Circumcision" question could not be used, while circumcision type could not be inferred from surveys which did not have a "Who performed the circumcision" and/or "Where was the circumcision performed" question.}
      \endfoot
      %%%%%%%%%%%%%%%%%%%%%%
      %%% Table contents %%%
      %%%%%%%%%%%%%%%%%%%%%%
      \multicolumn{2}{l}{\textbf{Angola}} \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Benin}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Botswana}} \\ 
& 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Burkina Faso}} \\ 
& 2003 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Burundi}} \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Cameroon}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Central African Republic}} \\ 
& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Chad}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Congo - Kinshasa}} \\ 
& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Côte d’Ivoire}} \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Eswatini}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
& 2010 (MICS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Ethiopia}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Gabon}} \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Gambia}} \\ 
& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Ghana}} \\ 
& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Guinea}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Guinea-Bissau}} \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Kenya}} \\ 
& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Lesotho}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2009 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2014 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Liberia}} \\ 
& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Malawi}} \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2013 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Mali}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Mozambique}} \\ 
& 2003 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2009 (AIS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Namibia}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Niger}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Nigeria}} \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Repulic of the Congo}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2009 (AIS) & \checkmark & \xmark & \checkmark & \xmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Rwanda}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2008 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Senegal}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Sierra Leone}} \\ 
& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{South Africa}} \\ 
& 2002 (HSRC) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2008 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2012 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Tanzania}} \\ 
& 2003 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2007 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2012 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Togo}} \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Uganda}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2011 (AIS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Zambia}} \\ 
& 2007 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Zimbabwe}} \\ 
& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark 
\end{longtable}
}

@@

Gaussian priors were assigned to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$. Gaussian priors were set for all correlation parameters on the logit scale, such that 
\begin{align*} 
  \hat{\rho}_{(\cdot)} = \frac{2}{1 + \exp(-\rho_{(\cdot)})} - 1 \sim N(3, 1^2)
\end{align*}
corresponding to 95\% CI prior weight that the autocorrelation parameters are between 0.48 and 0.99 on the real scale. For the age, district and age-district random effects, we assigned exponential priors on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$ on each of these processes. For the temporal, age-time and space-time random effects, the hyperpriors on the standard deviations $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}}$ were decided as part of the model calibration process (see Section \ref{sec::modelcheck} for further details).

>>>>

% \begin{landscape}
{\linespread{1}
  \footnotesize 
\begin{longtable}[c]{ll ccc c}
      %%%%%%%%%%%%%%%%%%%%
      %%% Table header %%%
      %%%%%%%%%%%%%%%%%%%%
      % Upper layer of table header
      \hline
      % Lines inside the header
      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
      \cmidrule(lr){5-6}
       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
      % Lower lines
      \hline
      \vspace{-3pt}
      \endhead
      %%%%%%%%%%%%%%%%%%%%
      %%% Table footer %%%
      %%%%%%%%%%%%%%%%%%%%
      \\[-3pt] \hline
      \endfoot
      %%%%%%%%%%%%%%%%%%%%%%
      %%% Table contents %%%
      %%%%%%%%%%%%%%%%%%%%%%
      \multicolumn{2}{l}{\textbf{Angola}} \\ 
& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Benin}} \\ 
& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
\multicolumn{2}{l}{\textbf{Botswana}} \\ 
& 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 
\end{longtable}
}

\begin{landscape}
\include{paper/figures/supp_figs/Survey_Table}
\end{landscape}

@@

Gaussian priors were assigned to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$. Gaussian priors were set for any correlation parameters on the logit scale, such that 
\begin{align*} 
  \hat{\rho}_{(\cdot)} = \frac{2}{1 + \exp(-\rho_{(\cdot)})} - 1 \sim N(3, 1^2)
\end{align*}
corresponding to 95\% CI prior weight that the autocorrelation parameters are between 0.48 and 0.99 on the real scale. For the age, district and age-district random effects, we assigned exponential priors on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$ on each of these processes. For the temporal, age-time and space-time random effects, the hyperpriors on the standard deviations $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}}$ were decided as part of the model calibration process (see Section \ref{sec::modelcheck} for further details).
